Topological Analysis of Bitcoin's Lightning Network

### 2019-01-16 article/main.tex
Clearing literature from github

A similar optimization strategy of robustness and connectivity \cite{shargel2003optimization} could be applied to LN as well. We leave it for future work to empirically assess the robustness and connectivity gains if strategy of \cite{shargel2003optimization} would be implemented in LN client implementations.

@@

\section{Conclusion}
In summary, a better understanding of the network topology is essential
for improving the robustness of complex systems, like LN. Networks' resilience depends on their topology. LN is well approximated by the scale-free model and also its attack tolerance properties are similar to those of scale-free networks; in particular, while LN is robust against random failures, it is quite vulnerable in the face of targeted attacks. 
High-level depictions of LN's topology, like Figure~\ref{fig:lntopology}, convey a false image of security and robustness. As we have demonstrated, LN is structurally weak against rational adversaries. Thus, to provide robust Layer 2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
\section{Acknowledgements}
We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.

>>>>

A similar optimization strategy of robustness and connectivity to that of \cite{shargel2003optimization} could be applied to LN as well. We leave it for future work to empirically assess the robustness and connectivity gains if strategy of \cite{shargel2003optimization} would be implemented in LN client implementations.

@@

\section{Conclusion}
In summary, a better understanding of the network topology is essential
for improving the robustness of complex systems, like LN. Networks' resilience depends on their topology. LN is well approximated by the scale-free model and also its attack tolerance properties are similar to those of scale-free networks; in particular, while LN is robust against random failures, it is quite vulnerable in the face of targeted attacks. 
High-level depictions of LN's topology, like Figure~\ref{fig:lntopology}, convey a false image of security and robustness. As we have demonstrated, LN is structurally weak against rational adversaries. Thus, to provide robust Layer-2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
\section{Acknowledgements}
We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.
